%--------------------------------------------%
%                Premble                     %
%--------------------------------------------%
\documentclass[letterpaper,10pt]{article}

\input{MyImport}
\usepackage{lmodern}

\newcommand{\BlockSkip}{1.5em}

\newenvironment{BlockList}
{\begin{list}{}{\setlength{\labelwidth}{1em}\setlength{\leftmargin}{4em}\setlength{\topsep}{0em}\setlength{\itemsep}{0.9em}}}
{\end{list}}

\newenvironment{BulletList}[1]{\begin{list}{#1}{\setlength{\labelwidth}{0.5em}\setlength{\leftmargin}{2.5em}\setlength{\topsep}{0em}\setlength{\itemsep}{0em}\setlength{\parsep}{0.3em}}}
{\end{list}}

\newenvironment{BlockBulletList}[1]{\begin{list}{#1}{\setlength{\labelwidth}{1em}\setlength{\leftmargin}{5em}\setlength{\topsep}{0em}\setlength{\itemsep}{0.1em}\setlength{\parsep}{0.3em}}}
{\end{list}}

\newcommand{\TheSectionHeaderBookmark}{}
\newcommand{\TheSectionHeaderTypeSet}{}
\newcommand{\Empty}{}

\newcommand{\SectionHeader}[2][]{    
    \textbf{\large{\StrLeft{#2}{1}{\small \StrGobbleLeft{#2}{1}}}}%
    \phantomsection
    \ifthenelse{\isempty{#1}}%
        {\addcontentsline{toc}{section}{#2}}%
        {\addcontentsline{toc}{section}{#1}}%
    \vspace*{0.1em}%
}

\newenvironment{SectionBlock}[2][]
    {\SectionHeader[#1]{#2}\rule{0.2em}{0em}\begin{BlockList}}
    {\end{BlockList}\rule{2em}{0em}}
    
\newenvironment{SectionBullet}[3][]{
    \SectionHeader[#1]{#2}\rule{0.2em}{0em}
    \begin{BlockBulletList}{#3}
}{
    \end{BlockBulletList}\rule{2em}{0em}
}

\newcommand{\InformationBlock}[1]{
    \let\BlockName#1
    \textbf{\large{}}
}

\newenvironment{Address}[1]{%
    \begin{minipage}[t]{0.3\linewidth}%
        \begin{center}%
            \textbf{#1}\\[0.1em]%
} {%
    \end{center}\end{minipage}%
}

\newcommand{\TheName}{}
\newcommand{\Email}[3]{
    \href{mailto:#1 #2 <#3>}{#3} 
}

\newcommand{\TheDegree}       {}
\newcommand{\TheTimeSpan}     {}
\newcommand{\TheUniversity}   {}
\newcommand{\TheDepartment}   {}
\newcommand{\Degree}       [1]{\renewcommand{\TheDegree}    {#1}}
\newcommand{\TimeSpan}     [1]{\renewcommand{\TheTimeSpan}  {#1}}
\newcommand{\University}   [1]{\renewcommand{\TheUniversity}{#1}}
\newcommand{\Department}   [1]{\renewcommand{\TheDepartment}{#1}}

\ArrayMake{Notes}
\newcommand{\Note}[1]{
    \ArrayPush{Notes}{#1}
}
\newcommand{\ListNotes}{
    \ifnum\value{NotesArrayCount}>0
        \begin{BulletList}{--}
            \For[1]{1}{\value{NotesArrayEnd}}{\item{\ArrayGet{Notes}{\value{ForLoopCounter}}}}
        \end{BulletList}
        \ArrayClear{Notes}
    \fi
}


\newcommand{\MakeDegreeItem}{
    \item{
        \textbf{\TheDegree} \dotfill \TheTimeSpan\\
        \textit{\TheUniversity}, \TheDepartment\hfill
        \ListNotes
    }
}

\newcommand{\Skip}[1][0.1em]{\\[#1]}
\let\NewLine\Skip


\newcommand{\Relap}{\textsc{Relap5}}
\newcommand{\Melcor}{\textsc{Melcor}}

\setstretch{1.2}

% ====================================================================================== %
%                                           Document                                     %
% ====================================================================================== %
\begin{document}

\pagestyle{empty}

% ================================================== %
%                      Name                          %
% ================================================== %
\begin{center}
    \Large{\textsc{Troy C. Haskin}}
    \rule[1.1em]{\linewidth}{0.05em}
\end{center}\vspace{-2.6em}

{
    \centering
    1500 Engineering Drive          \\[-0.20em]
    841 Engineering Research Bldg.  \\[-0.20em]
    Madison, WI 53706               \\[-0.20em]
    608.265.4056                    \\[-0.20em]
    \Email{Troy}{Haskin}{haskin@wisc.edu}

}
\null\vspace{0.50em}


% ================================================== %
%                    EDUCATION                       %
% ================================================== %
\begin{SectionBlock}[Education]{EDUCATION}
%
%
% PhD NE
%
    \Degree{Ph.D. Nuclear Engineering}
    \University{University of Wisconsin--Madison}
    \Department{Department of Engineering Physics}
    \TimeSpan{September 2008 -- Present}
    \Note{Concurrently received B.S. and M.S. in Nuclear Engineering from UW--Madison in May 2011}
    \Note{Graduate GPA: 3.68 / 4.0; Undergraduate GPA: 3.24 / 4.0 }
    \Note{Currently focused on modeling a UW--Madison experiment involving a low pressure, natural circulation water loop with radiant heating; investigating the stability of the system under various conditions.}
    \MakeDegreeItem
%
%
% MS ME
%    
    \Degree{M.S. Mechanical Engineering}
    \Department{Mechanical Engineering}
    \TimeSpan{September 2009 -- May 2012}
    \Note{GPA: 3.80 / 4.0}
    \Note{Acquired through course work with an emphasis on thermohydraulic theory.}
    \MakeDegreeItem
%
%
% BSMS NE
%
    %\Degree{B.S./M.S Nuclear Engineering}
    %\Department{Department of Engineering Physics}
    %\TimeSpan{September 2004 -- September 2009}
    %\Note{Undergraduate GPA: 3.24 / 4.0; Master's GPA: 3.34 / 4.0}
    %\Note{Senior design: documentation, verification, and validation for a RELAP5 model of a General Atomics high temperature, prismatic reactor.}
    %\MakeDegreeItem
%
%
% Japanese Certificate
%
    \Degree{Japanese Technical Communications Certificate}
    \Department{Department of Engineering Professional Development}
    \TimeSpan{September 2006 -- May 2008}
    \Note{Four semesters of conversational Japanese}
    \Note{Two semesters of technical Japanese vocabulary and translations for a variety of scientific fields.}
    \MakeDegreeItem
\end{SectionBlock}


% ================================================== %
%                    Employment                      %
% ================================================== %
\begin{SectionBlock}[Employment]{EMPLOYMENT}
%
% RA
%
     \item {\textbf{Research Assistant} \dotfill September 2008 -- Present\\
               \textit{University of Wisconsin--Madison}, Department of Engineering Physics \hfill
          \begin{BulletList}{--}
               \item {Researching the thermohydraulic behavior of air and water-cooled (single and two-phase) cooling 
                      systems for next generation reactors with an emphasis on system stability.}
               \item {System modeling with \Melcor{} for the cooling systems and experimental setups at the university.}
               \item {Mentoring new students in modeling various problems in both \Relap{} and \Melcor{}.}
          \end{BulletList}
     }
%
% SNL
%
     \item{\textbf{Summer Intern} \dotfill Summer 2011\\
               \textit{Sandia National Laboratories}, Severe Accident Modeling \hfill
               \begin{BulletList}{--}
                    \item {Coupled air-cooled and water-cooled Reactor Cavity Cooling System designs with a full-scale pebble bed \Melcor{} model; 
                           updated a modular reactor \Melcor{} model to reflect current, anticipated design.}
                    \item {Performed several accident scenarios for both core models.}
               \end{BulletList}
     }
%
% ANL
%
     \item{\textbf{Summer Intern} \dotfill Summer 2008\\
               \textit{Argonne National Laboratory}, Nuclear Engineering Division \hfill
               \begin{BulletList}{--}
                    \item {Performed documentation, verification, and validation for a \Relap{} model of a General Atomics high temperature, prismatic reactor.}
                    \item {Modeled several anticipated transients without SCRAM and analyzed results.}
               \end{BulletList}
     }
\clearpage
%
% NE 411
%
\item{\textbf{Class Lecturer} \dotfill Fall 2013\\
               \textit{University of Wisconsin--Madison}, Department of Engineering Physics \hfill
               \begin{BulletList}{--}
                    \item {Senior level class that aims to utilize all previous student experience for analysis and understanding of various reactor systems and components under a wide range of operation conditions.}
                    \item{ Topics covered: defense-in-depth, thermomechanical stress analysis, LWR thermohydraulics, two-phase flow fundamentals, LWR accident scenarios, power cycle analysis, core thermal design, and introduction to advanced reactors designs.}
                    \item {Prepared and presented lectures, homework, and exams.}
               \end{BulletList}
     }
%
% Tutor
%     
     \item {\textbf{Undergraudate Tutor} \dotfill     January 2007 -- Present \\
        \textit{University of Wisconsin--Madison}, Undergraduate Learning Center \hfill 
        \begin{BulletList}{--}
            \item {Helping students understand concepts more deeply and develop problem solving strategies for the introductory and intermediate engineering classes.}
            \item {Classes covered include: Thermohydraulics, Heat Transfer, Calculus, Linear Algebra, and others.}
        \end{BulletList}
     }
\end{SectionBlock}



%--------------------------------------------%
%                Notable Classes             %
%--------------------------------------------%
\begin{SectionBullet}[Notable Classes]{NOTABLE CLASSES}{--}
    \item {Computational Fluid Dynamics (wrote 2D, incompressible solver in \textsc{Matlab})}
    \item {Monte Carlo (Theory and MCNP5)}
    \item {Uncertainty and error propagation}
    \item {Two-phase and turbulent momentum/heat transfer}
    \item {Numerical methods for hyperbolic and elliptic systems (e.g., Godunov methods, Continuous and Discontinuous Galerkin methods)}
\end{SectionBullet}




%--------------------------------------------%
%             Computer Experience            %
%--------------------------------------------%
\begin{SectionBullet}[Computer Experience]{COMPUTER EXPERIENCE}{--}
    \item {Code Examples: \href{https://github.com/troyhaskin?tab=repositories}{My GitHub Repositories}}
    \item {Programming:  Fortran 90/95, \textsc{Matlab}}
    \item {System Analysis Programs: \Relap{}, \Melcor{}}
    \item {Operating systems: Windows and Unix-like/Linux (minor experience)}
    \item {Productivity Suites: Microsoft Word, OpenOffice.org, Google Docs}
    \item {Miscellaneous: \LaTeX{}, Git/GitHub, Mathematica, EES, PHP, HTML/CSS, XML}
    \item {Minor Experience: C, C++, XSLT, and JavaScript (including jQuery and Google Apps Script)}
\end{SectionBullet}




%--------------------------------------------%
%             Involvement                    %
%--------------------------------------------%
\begin{SectionBullet}[Involvement]{INVOLVEMENT}{--}
    \item {Membership: ANS National}
    %\item {SIAM-UW President (2011--2012)}
    \item {Communications officer: 
                ANS-UW Student Section  (2008--2009),
                WIN-UW Student Section  (2008--2009),
                SIAM-UW Student Section (2010--2011)
    }
    \item {Webmaster: 
            ANS-UW Student Section (2008--2010),
            WIN-UW Student Section (2008--2010),
            SIAM-UW Student Section (2010--2011),
            Oak Ridge/Knoxville ANS Local Section (2011)
    }
\end{SectionBullet}


\begin{SectionBullet}[Publications]{PUBLICATIONS}{--}
    \item{
        Lisowski, D. D., Haskin, T. C., Tokuhiro, A., Anderson, M. H., \& Corradini, M. L. (2013).
        Study on the Behavior of an Asymmetrically Heated Reactor Cavity Cooling System with Water in Single Phase.
        Nuclear Technology, 183(1), 75-87.
    }
\end{SectionBullet}



\end{document}





